Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-14 chi2012.tex
added subsections to discussion

% processes

>>>>

\subsection{Better Supporting the Task}

- are people more thorough
- do they evaluate more sources

\subsection{Causing Less Frustration}

- Gave up with aspects of the tasks later / not at all
- With websites, users gave up on websites and moved on early

\subsection{Keeping an Open Mind}

- Did users rule out choices less/later
- Did that mean they chose "better" options

\subsection{What method did people use?}

- Processes
- Organisation of data/screen
- A vs B, how are they different?

% DAN's  qual analysis of processes
